Sparse spectral methods for partial differential equations on spherical caps

### 2021-05-20 papers/spherical-caps/revised/spherical-caps.tex

There are of course other approaches for solving PDEs on surfaces, such as the closest point method \cite{macdonald2010implicit, macdonald2008level}. This involves recasting the PDE as one involving a \enquote{closest point} operator in a 3D volume that acts as a \enquote{shell} for the surface. While such an approach is useful for other geometries, it is of low order and does not achieve spectral convergence with sparse discretisations. Further, for our interest of the sphere, it would not take advantage of any rotational symmetry to achieve optimal complexity with a direct solver.

>>>>

There are of course other approaches for solving PDEs on surfaces, such as the closest point method \cite{macdonald2010implicit, macdonald2008level}. This involves recasting the PDE as one involving a \enquote{closest point} operator in a 3D volume that acts as a \enquote{shell} for the surface. While such an approach is useful for other geometries, it is of low order and does not achieve spectral convergence with sparse discretisations. Further, for our domain of interest, the closest point method does not take advantage of any rotational symmetry, and so is unable to achieve optimal complexity with a direct solver.
